% !TEX program = xelatex

\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}
\usepackage{verbatim}

\begin{document}
\header{}{geoffrey liu}
       {web developer, student at university of washington}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Contact details available upon request
    ~
    \href{mailto:main@g-liu.com}{main@g-liu.com}
    \href{http://g-liu.com}{http://g-liu.com}
    Github: \href{http://github.com/g-liu}{g-liu}
  \section{programming}
  	JavaScript, jQuery
  	Java
  	PHP
  	Ruby on Rails
    HTML, CSS tools
  \section{tools}
    WordPress
    JUnit testing
    git, svn
  \section{coursework}
    Java programming
    Web programming
    Data structures
    Software design
    HW/SW Interface
    Linux tools
    Music Theory
  \section{languages}
    English
    Chinese
    French
  \section{interests}
    UI/UX design
    Teaching
    Blogging
    Classical music
\end{aside}

\section{education}

\begin{entrylist}
  \entry
    {since 2012}
    {Computer Science, Piano Performance}
    {U. of Washington, Seattle}
    {Direct admission into Computer Science, 2012 \\
    Dean's List candidate, 2012-2014 \\
    3.64 overall GPA \\
    2017 expected graduation}
\end{entrylist}

\section{work experience}

\begin{entrylist}
  \entry 
    {2014}
    {Programming Intern, Seattle Publishing}
    {Internship}
    {Develop a Ruby on Rails website for \href{http://seattlepublishing.com}{Seattle Publishing}. Increased compatibility with IE8, especially SVG graphics and responsiveness. Implemented Bootstrap components for responsiveness. Migrate site from Rails 3 to Rails 4, updating legacy code and integration tests.}
  
  \entry
    {2014}
    {Webmaster, ASUW}
    {Part-time}
    {Develop and maintain WordPress sites for the Associated Students of the University of Washington (ASUW). Write custom plugins with admin settings backend. Develop a completely customized WordPress theme for the main site at \href{http://asuw.org}{ASUW.org}.}
\end{entrylist}

\section{projects}

\begin{entrylist}
  %\entry
  %  {May 2012}
  %  {Sudoku solver}
  %  {AP Computer Science}
  %  {\bullet \, Wrote a Sudoku solver in Java \\
  %  \bullet \, Used JLabels to emulate an actual Sudoku puzzle \\
  %  \bullet \, Took advantage of recursive brute-force solving}
  \entry
    {2014}
    {ASUW Jobs site development}
    {\href{http://jobs.asuw.org}{ASUW.org}}
    {\bullet \, Collaborated with Mitchell (co-worker) and Office of Communications to deploy a new Jobs website within three weeks. \\
    \bullet \, Developed custom, responsive, print-ready admin back-end interfacing with MySQL database, to track job applications. \\
    \bullet \, Used Bootstrap, dead-simple-grid for responsive layout, HTML5/jQuery front-end validation, PHP back-end validation, sanitization on application form.
    }
  \entry
    {Winter 2014}
    {CSE 332 - Various projects}
    {}
    {\bullet \, Made a Census Data analyzer to tally population in a given area of the United States. Has GUI and CLI. Multi-thread capable. \\
    \bullet \, Implemented different sorting algorithms, data structures to analyze text from plays. Extensively tested with JUnit. \\
    \bullet \, Collaborated with partner using git development and Eclipse IDE. All code rigorously documented with javadoc.}
  \entry
    {Oct. 2013}
    {Website makeover, Seattle GiveCamp}
    {\href{http://changestreammedia.org}{ChangeStreamMedia.org}}
    {\bullet \, Trained team members on using the WordPress CMS \\
    \bullet \, Customized existing WordPress theme with CSS and PHP \\
    \bullet \, Researched viewer audience, statistics. Performed SEO, boosting traffic almost immediately}
  %\entry
  %  {ongoing}
  %  {Personal website overhaul}
  %  {\href{http://g-liu.com}{G-liu.com}}
  %  {\bullet \, Scrapped old website, rewrote entire website \href{http://g-liu.com/scratch}{from scratch} \\
  %  \bullet \, Experimented with making basic web applications (see \href{http://g-liu.com/sandbox}{\texttt{/sandbox}}) \\
  %  \bullet \, Made website mobile-compatible with CSS media queries \\
  %  \bullet \, Continuing to maintain personal WordPress blog: includes theme development via PHP and WordPress}
\end{entrylist}

\pagebreak

\section{references}

Available upon request.

\end{document}
